\chapter*{Preface}
\addcontentsline{toc}{chapter}{Preface}
For me, finding a thesis topic was no easy task. All I knew was: "I want to build something cool". So when it was time to select the topic, I decided the best course of action was to visit the professors who gave the most interesting lectures. When I went to visit the Embedded Software Group on the 9th floor of EEMCS and learned about the world of Visible Light Communication (VLC), I knew I found the right topic.

The basic concept of VLC was familiar to me. "It's just really fast morse code", is a sentence I used a lot to explain VLC to my friends. When I noticed that my (non-technical) friends could not grasp this concept, I was sure that I could help create to something innovative and new. With this motivation I started the \textit{Dark Sensing} project.

\vspace{1\baselineskip}

\noindent
The Dark Sensing project has learned me a lot the last year. Even though finishing the project took longer than expected and wasn't always a fun activity, I'm happy that im finaly done and am happy with the result. This thesis would not look the same without the help of some persons who need to be thanked. First of all, I need to thank Marco for supervising the project. Even though our opinions where not always aligned, without his guidance the project would not have been this successful. I also need to thank Rens and the rest of the VLC power group for their help for their ideas and general feedback. I also thank my house-mates for their help. Finally I want to thank my friends an family for their support while I was working on my master thesis.

\vspace{1\baselineskip}

\noindent
Hajo Kleingeld

\vspace{1\baselineskip}

\noindent
Delft, The Netherlands

\noindent
12th December 2017
